Differential expression analysis: A pipeline to analyse time-course gene expression data

### 2019-03-01 scripts/02_differential_expression_analysis.Rmd
ENH Every DE related method now take limma contrasts

FIXME add estimation of log fold change.

```{r de_analysis}
# Define contrast
de_analysis = data.frame(row.names=row.names(data))
for(contrast_formula in timecourse_contrasts){
    contrast = limma::makeContrasts(
	contrasts=contrast_formula,
	levels=levels(meta$Group))
    model = moanin::timecourse_differential_expression_analysis(
	as.matrix(data), meta, contrast)
    contrast_name = gsub(" ", "", contrast_formula, fixed=TRUE)
    contrast_name_pval = paste(contrast_name, "-pval", sep="")
    contrast_name_qval = paste(contrast_name, "-qval", sep="")
    de_analysis[contrast_name_pval] = model$pval_lrt
    de_analysis[contrast_name_qval] = model$qval_lrt

    # Now compute log fold change using different methods
    # XXX This fails very badly if the contrasts provided is wrong.
    log_fold_change_epicon = moanin::estimate_log_fold_change(
	data, meta, c(contrast_formula), method="epicon")
    contrast_name_lfc_epicon = paste(contrast_name, "-lfc_epicon", sep="")
    de_analysis[contrast_name_lfc_epicon] = log_fold_change_epicon

    # XXX Something is wrong with method max
    log_fold_change_max = moanin::estimate_log_fold_change(
	data, meta, c(contrast_formula), method="max")
    contrast_name_lfc_max = paste(contrast_name, "-lfc_max", sep="")
    de_analysis[contrast_name_lfc_max] = log_fold_change_max

pvalues = de_analysis
```

@@

pvalue = de_analysis[, "M-K-qval"]
lfc_epicon = de_analysis[, "M-K-lfc_epicon"]

>>>>

```{r de_analysis}
# Define contrast
contrasts = limma::makeContrasts(
	contrasts=timecourse_contrasts,
	levels=levels(meta$Group))

pvalues = moanin::timecourse_differential_expression_analysis(
    data, meta, contrasts)
qvalues = apply(pvalues, 2, stats::p.adjust)

log_fold_change_epicon = moanin::estimate_log_fold_change(
    data, meta, contrasts,  method="epicon")

log_fold_change_max = moanin::estimate_log_fold_change(
    data, meta, contrasts, method="max")
```

@@

pvalue = qvalues[, "M-K"]
lfc_epicon = log_fold_change_epicon[, "M-K"]
